### 2012-03-08 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

According to \cite{Mlynkova:2008:AAX:1494650.1495496}, the type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods \cite{Chidlovskii:2002:SEX:544220.544288, Garofalakis:2000:XSE:342009.335409, Moh:2000:RSW:336597.336638, Wong03onstructural, Vosta:2008:EAC:1802514.1802522} are based on experience with manual construction of schemas, motivated by real-world usages of XML schema, and their result commonly does not belong to any class of grammar. Two of these approaches are described in Chapter \ref{section_xtract} and Chapter \ref{section_even_an_ant_can_create_an_xsd} \todo{někde Chapter, někde Section - sjednotit a dodržovat}. The former one incorporates so-called MDL principle to create the (sub)optimal result. The latter one combines several verified methods together to improve the quality of the result.

@@

\section{Common Caracteristics}
The process of XML schema inference commonly used by a significant number of approaches is summarized in \cite{Mlynkova:2008:AAX:1494650.1495496} as the following one: For each occurrence of element $e$ from the input XML documents and its subelements $e_1, e_2, ..., e_k$ a production $e \rightarrow e_1 e_2 ... e_k$ is constructed. The productions form so-called \emph{initial grammar} (IG). For each element type the productions are then merged, simplified and generalized using various methods and criteria. A common approach is so-called \emph{merging state algorithm}, where a \emph{prefix tree automaton} (PTA) is built from the productions of the same element type and the automaton is generalized via merging of its states. Finally, the generalized automaton/grammar is expressed in syntax of the respective XML schema language.
\todo[inline]{Q: Tento odstavec je doslovne prebraty z uvedeneho clanku. Mozem to takto pouzit? A: ano, jen by pak neměla být výrazně jiná úroveň angličtiny}

>>>>

According to \cite{Mlynkova:2008:AAX:1494650.1495496}, the type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods \cite{Chidlovskii:2002:SEX:544220.544288, Garofalakis:2000:XSE:342009.335409, Moh:2000:RSW:336597.336638, Wong03onstructural, Vosta:2008:EAC:1802514.1802522} are based on experience with manual construction of schemas, motivated by real-world usages of XML schema, and their result commonly does not belong to any class of grammar. Two of these approaches are described in Chapter \ref{section_xtract} and Chapter \ref{section_even_an_ant_can_create_an_xsd}. The former one incorporates so-called MDL principle to create the (sub)optimal result. The latter one combines several verified methods together to improve the quality of the result.

@@

\section{Common Caracteristics}
The process of XML schema inference commonly used by a significant number of approaches is summarized in \cite{Mlynkova:2008:AAX:1494650.1495496} as the following one: For each occurrence of element $e$ from the input XML documents and its subelements $e_1, e_2, ..., e_k$ a production $e \rightarrow e_1 e_2 ... e_k$ is constructed. The productions form so-called \emph{initial grammar} (IG). For each element type the productions are then merged, simplified and generalized using various methods and criteria. A common approach is so-called \emph{merging state algorithm}, where a \emph{prefix tree automaton} (PTA) is built from the productions of the same element type and the automaton is generalized via merging of its states. Finally, the generalized automaton/grammar is expressed in syntax of the respective XML schema language.
